% Footer Formatting: DO NOT CHANGE -----------------------------------
\fancyfoot{}

\fancyfoot[LE]{\colorbox{urban-footergray}{\makebox(0.2, 0.12)[r]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase{}\hspace{0.2in}}}}\colorbox{urban-gold}{\makebox(0.2, 0.12)[c]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase\thepage}}}\colorbox{urban-footergray}{\makebox(5.64, 0.12)[r]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase{\so{Acknowledgments}}\hspace{0.2in}}}}}

\fancyfoot[RO]{\colorbox{urban-footergray}{\makebox(5.64, 0.12)[l]{\fontsize{7.5}{0}\selectfont\bfseries{\hspace{0.2in}\MakeUppercase{\so{Acknowledgments}}}}}\colorbox{urban-gold}{\makebox(0.2, 0.12)[c]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase\thepage}}}\colorbox{urban-footergray}{\makebox(0.2, 0.12)[r]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase{}\hspace{0.2in}}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Acknowledgments %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{Acknowledgments}

This report was funded by the Alfred P. Sloan Foundation and National Science Foundation National Center for Science and Engineering Statistics. We are grateful to them and to all our funders, who make it possible for Urban to advance its mission. 

The views expressed are those of the authors and should not be attributed to the Urban Institute, its trustees, or its funders. Funders do not determine research findings or the insights and recommendations of Urban experts. Further information on the Urban Institute’s funding principles is available at urban.org/fundingprinciples.

We would like to thank our collaborators at the Internal Revenue Service Statistics of Income Division, especially Barry Johnson and Victoria Bryant, for their amazing support for this project. We also thank our stellar validation server project team, consisting of Leonard Burman, John Czajka, Surachai Khitatrakun, Graham MacDonald, Rob McClelland, Silke Taylor, Kyle Ueyama, Doug Wissoker, and Noah Zwiefel. Thank you to Gabriel Morrison for reviewing our code.

Finally, we thank our advisory board, who have provided invaluable advice throughout the course of this project. The members are John Abowd, Jim Cilke, Jason DeBacker, Nada Eissa, Rick Evans, Dan Feenberg, Max Ghenis, Nick Hart, Matt Jensen, Barry Johnson, Ithai Lurie,  Shelly Martinez, Robert Moffitt, Amy O'Hara, Jerry Reiter, Emmanuel Saez, Wade Shen, Aleksandra Slavkovi\'c, Salil Vadhan, and Lars Vilhuber.