% Footer Formatting: DO NOT CHANGE -----------------------------------
\fancyfoot{}

\fancyfoot[LE]{\colorbox{urban-footergray}{\makebox(0.2, 0.12)[r]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase{}\hspace{0.2in}}}}\colorbox{urban-gold}{\makebox(0.2, 0.12)[c]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase\thepage}}}\colorbox{urban-footergray}{\makebox(5.64, 0.12)[r]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase{\textls{About the Authors}}\hspace{0.2in}}}}}

\fancyfoot[RO]{\colorbox{urban-footergray}{\makebox(5.64, 0.12)[l]{\fontsize{7.5}{0}\selectfont\bfseries{\hspace{0.2in}\MakeUppercase{\textls{About the Authors}}}}}\colorbox{urban-gold}{\makebox(0.2, 0.12)[c]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase\thepage}}}\colorbox{urban-footergray}{\makebox(0.2, 0.12)[r]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase{}\hspace{0.2in}}}}}
% Footer Formatting: DO NOT CHANGE -----------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% About Author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{About the Authors}

\textbf{Andr\'es F. Barrientos} is an assistant professor of statistics at Florida State University. His research interests focus on developing and studying methodological procedures in statistical science that incorporate flexible Bayesian modeling and approaches for data privacy. His methodological research involves single and regression density estimation, hypothesis testing, massive data, probabilistic approaches for complex data, differentially private procedures, and synthetic data generators.

Barrientos obtained his PhD in statistics at the Pontificia Universidad Catolica de Chile, in Chile. Previously, he was a postdoctoral associate in the department of statistical science at Duke University, under the mentoring of Dr. Jerry Reiter. 

\noindent\textbf{Aaron R. Williams} Aaron R. Williams is a senior data scientist in the Income and Benefits Policy Center and Program on Retirement Policy at the Urban Institute, where he works on retirement policy, microsimulation models, data privacy, and data imputation methods. He has worked on Urban’s Dynamic Simulation of Income microsimulation model, the Social Security Administration’s Modeling Income in the Near Term microsimulation model, and the Tax Policy Center’s synthesis of individual tax records.

% Williams leads Urban’s R Users Group and assists researchers across Urban with projects that use R for data science, statistical analysis, data visualization, mapping, and automation.

Williams is an adjunct professor in the McCourt School of Public Policy at Georgetown University. He holds a BS in economics from Virginia Commonwealth University, a BA in music from Virginia Commonwealth University, and an MS in mathematics and statistics from Georgetown University.

\noindent\textbf{Joshua Snoke} a statistician at RAND. His primary research focuses on novel estimation procedures when data are unavailable because of privacy restrictions. These methods seek to increase researchers’ ability to answer policy questions using hard to obtain data due to privacy concerns. He has expertise broadly in the field and has published papers on topics such as the release of synthetic datasets, the enabling of model estimation across multiple databases, and the creation of differentially private algorithms.

% His work, both privacy related and otherwise, has involved a variety of administrative datasets, such as from the US Census Bureau, the UK Administrative Data Research Network, the US Army Recruiting Command, and the American Educator Panels. His broader methodological interests include estimation, model selection, nonparametric modeling and classification, machine learning, and causal inference.

Snoke received his BS in mathematics and economics from Wheaton College. He received his PhD in statistics with a graduate minor in social data analytics from the Pennsylvania State University.

\noindent\textbf{Claire McKay Bowen} is the lead data scientist of privacy and data security at the Urban Institute. Her research focuses on assessing the quality of differentially private data synthesis methods and science communication. In 2021, the Committee of Presidents of Statistical Societies identified her as an emerging leader in statistics for her technical contributions and leadership to statistics and the field of data privacy and confidentiality.

Bowen holds a BS in mathematics and physics from Idaho State University and an MS and PhD in statistics from the University of Notre Dame. After completing her PhD, she worked at Los Alamos National Laboratory, where she investigated cosmic ray effects on supercomputers.